% !TeX spellcheck = en_GB
%%=============================================================================
%% Conclusie
%%=============================================================================
\chapter{\IfLanguageName{dutch}{Conclusie}{Conclusion}}
\label{ch:conclusie}

% Trek een duidelijke conclusie, in de vorm van een antwoord op de onderzoeksvra(a)g(en).
% Wat was jouw bijdrage aan het onderzoeksdomein en
% hoe biedt dit meerwaarde aan het vakgebied/doelgroep? 
% Reflecteer kritisch over het resultaat. 
% Had je deze uitkomst verwacht? 
% Zijn er zaken die nog niet duidelijk zijn?
% Heeft het onderzoek geleid tot nieuwe vragen die uitnodigen tot verder onderzoek?

%%Research question
%What are the advantages and disadvantages of a migration from Windows Server 2016 to Windows Server 2019 in a business environment?
%%Sub-research question
%What are the differences between the Windows, ServerCore and Nano Server Base Container Images of Windows Server 2019?
%Can SAP be migrated from an existing Windows Server 2016 to Windows Server 2019 in a business environment?
%How can the new features of Windows Server 2019 be leveraged in the migrated infrastructure? 

The final conclusion of this bachelor's thesis is that a migration to Windows Server 2019 is achievable.
While a migration to Windows Server 2019 in an environment with a third-party application requires additional research, it was attainable for an SAP environment. 
The migration from Windows Server 2016 to Windows Server 2019 is also feasible for any organization running an \acrshort{eol} \acrshort{os}, as expected with the latest version of the \acrshort{os}.
This for either the general \acrshort{os} and the base container images.
Windows Server 2019 offers a wide array of improvements in terms of security, hybrid cloud, application platform and the \acrfull{hci}.
%It makes the organizations environment future-proof. 
The addition of the new Windows base container image provides the tools for automated \acrshort{ui} tests and its additional dependencies make it perfect for utilization with out-of-date packages. 
The Server Core base container image can be used to run typical Windows services. 
It offers application compatibility and has a wide array of built-in Windows roles and features. 
The Nano Server base container image was designed for 'born in the cloud' applications that provide an agile deployment and offer on-demand availability. 
The reduced footprint of the base container images without a drop of performance make the latest version the natural choice. 
The new features which are introduced can be leveraged through the usage of the \acrfull{wac}.
Organizations that are running \acrshort{eol} \acrlong{os}s should consider the migration to Windows Server 2019.
Organizations that are running \acrshort{eol} infrastructure could also consider a migration to the cloud, although this imposes additional research towards the advantages of a cloud solution in comparison to an in-house infrastructure.
