% !TeX spellcheck = en_GB
%%=============================================================================
%% Voorwoord
%%=============================================================================

\chapter*{\IfLanguageName{dutch}{Woord vooraf}{Preface}}
\label{ch:voorwoord}

Throughout the following pages, I will research the question: 'What are the advantages and disadvantages of a migration from Windows Server 2016 to Windows Server 2019 in a business environment?'. 
This bachelor's thesis was written in the context of my graduation at the University College Ghent where I studied Applied Computer Sciences and by order of delaware, where I researched and wrote my bachelor's thesis from February 2019 till June 2019.

In consultation with my promoter, Ludwig Stroobant, and my co-promoter, Glenn Verschuere, the research question was formulated as the basis. 
For the duration of this assignment, they were always there to answer the questions I had regarding the research. 
In addition, I would like to thank Kasper Heyndrickx. 
His technical knowledge of SAP was of immense importance for this bachelor's thesis.

I would like to thank them. 
Without them, this would not have been possible.
Furthermore, I would like to give a special thanks to delaware and especially to Tomas Castro and Jonas Decoster. 
Without their effort, I would never have had the opportunity to do this research from their branch in Harbin, China.
I would also like to thank Henry Hao and Cici Chen for their hospitality and guidance during my stay.
It was an experience I will never forget and always be grateful for. 

Finally, I would like to thank my parents. Their wisdom and motivating words have helped me to bring this bachelor's thesis to a successful conclusion.\\
I wish you a lot of reading pleasure.

Jens Du Four

Ghent, 31/05/2019